### 2016-12-23 README.Rmd
Merge branch 'master' into devel
* master: (27 commits)
  Fix MS level test in quantify,OnDiskMSnExp to support MS2+ level quantitation
  add onDisk vs inMem addId data unit test
  add covr r dep
  remove codecov bash script as build fails/timeouts
  run codecov bash script
  trigger check and codecov
  add codecov shield
  udpate readme with build status
  add link to coc
  remove some latex pkgs not present in repo
  add code of conduct
  all latex package deps
  add BiocStyle dep to hopefully address all latex deps
  add parnotes dep
  add tex dependency
  but before_install first
  ass tlm

```{r env, echo=FALSE}
knitr::opts_chunk$set(comment=NA)
```

`MSnbase` is an R/Bioconductor package that provides infrastructure
for plotting, data manipulation and processing of MS-based proteomics
data. The project was started by
[Laurent Gatto](http://lgatto.github.io/) in October 2010 (Mon Oct 4
23:35:23 2010, according to the git log) and has, since then,
benefited from various contributions.

```{r, echo=FALSE}
auth <- packageDescription("MSnbase")$Author
auth <- sub("<lg390@cam.ac.uk> ", "", auth)
auth <- gsub("\n\t", "\n", auth)
auth <- gsub("\t", " ", auth)
cat(auth, "\n")
```

@@

To install `MSnbase`

@@

If you need the github version

@@

## Build status

@@

General questions should be asked on the
[Bioconductor support forum](https://support.bioconductor.org/), using
`MSnbase` to tag the question.

@@

To cite the MSnbase package in publications, please use:

@@

Contributions to the package are more than welcome. If you want to
contribute to this package, you should follow the same conventions as
the rest of the functions whenever it makes sense to do so. Feel free
to get in touch (preferable opening a
[github issue](https://github.com/lgatto/MSnbase/issues/)) to discuss
any suggestions. The
[`MSnbase` development vignette](http://bioconductor.org/packages/devel/bioc/vignettes/MSnbase/inst/doc/MSnbase-development.pdf)
gives some background on the class infrastructure.

>>>>

```{r env, echo=FALSE}
suppressPackageStartupMessages(library("BiocStyle"))
knitr::opts_chunk$set(comment=NA)
```

`r Biocpkg("MSnbase")` is an R/Bioconductor package that provides
infrastructure for plotting, data manipulation and processing of
MS-based proteomics data. The project was started by
[Laurent Gatto](http://lgatto.github.io/) in October 2010 (Mon Oct 4
23:35:23 2010, according to the git log) and has, since then,
benefited from
[various contributions](http://lgatto.github.io/msnbase-contribs/).

@@

To install `r Biocpkg("MSnbase")`

@@

If you need the github version (not recommended unless you know what
you are doing)

@@

@@

General questions should be asked on the
[Bioconductor support forum](https://support.bioconductor.org/), using
`MSnbase` to tag the question. Feel also free to open a GitHub
[issue](https://github.com/lgatto/MSnbase/issues).

@@

To cite the `MSnbase` package in publications, please use:

@@

Contributions to the package are more than welcome. If you want to
contribute to this package, you should follow the same conventions as
the rest of the functions whenever it makes sense to do so. Feel free
to get in touch (preferable opening a
[github issue](https://github.com/lgatto/MSnbase/issues/)) to discuss
any suggestions. The
[`MSnbase` development vignette](http://lgatto.github.io/MSnbase/articles/MSnbase-development.html)
gives some background on the class infrastructure.
